\bf Landslide: Systematic Exploration for Kernel-Space Race Detection

### 2012-05-31 rv/paper.tex
start writing for RV

\documentclass[12pt]{book}
%\usepackage{amsmath,amsthm,amssymb,fullpage,yfonts,graphicx,proof,subfig,wrapfig,appendix,hyperref,mdwlist,wasysym}
\usepackage{amsmath,amsthm,amssymb,fullpage,yfonts,graphicx,proof,appendix,hyperref,mdwlist,wasysym}
\usepackage{upgreek}
%\usepackage{times}
\usepackage[charter]{mathdesign}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{epsfig}
\usepackage[bottom]{footmisc}
\usepackage{mjz-titlepage}
\usepackage{framed}
\usepackage{setspace}
\setstretch{1.05}
\usepackage{subfig}
\usepackage{changebar}
\usepackage{colortbl}
\usepackage{wrapfig}

@@

\input{titlepage}

\newcommand\true{\;\textit{true}}
\newcommand\false{\;\textit{false}}

@@

\begin{abstract}
Systematic exploration is an approach to finding race conditions by deterministically executing every possible interleaving of thread transitions and identifying which ones expose bugs.
Current systematic exploration techniques are suitable for testing user-space programs, but are inadequate for testing kernels, where the testing framework's control over concurrency is more complicated.

We present Landslide, a systematic exploration tool for finding races in kernels.
Landslide targets Pebbles, the kernel specification that students implement in the undergraduate Operating Systems course at Carnegie Mellon University (15-410).
We discuss the techniques Landslide uses to address the general challenges of kernel-level concurrency, and we evaluate its effectiveness and usability as a debugging aid.
We show that our techniques make systematic testing in kernel-space feasible and that Landslide is a useful tool for doing so in the context of 15-410.
\end{abstract}

\tableofcontents
\input{acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\input{related} % COMPLETE!
\input{challenges} % COMPLETE!
\input{terminology} % almost complete
\input{design}
\input{using}
\input{evaluation}
\input{futurework}
\input{conclusion}

% TODO: read presubmit.txt and check everything off

\bibliography{citations}{}
\bibliographystyle{alpha}

\appendix
\input{testcases}

>>>>

\documentclass{llncs}
%\usepackage{amsmath,amsthm,amssymb,fullpage,yfonts,graphicx,proof,subfig,wrapfig,appendix,hyperref,mdwlist,wasysym}
%\usepackage{amsmath,amsthm,amssymb,fullpage,yfonts,graphicx,proof,appendix,hyperref,mdwlist,wasysym}
\usepackage{upgreek}
%\usepackage{times}
%\usepackage[charter]{mathdesign}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{epsfig}
\usepackage[bottom]{footmisc}
%\usepackage{mjz-titlepage}
\usepackage{framed}
\usepackage{setspace}
\setstretch{1.05}
\usepackage{subfig}
\usepackage{changebar}
\usepackage{colortbl}
\usepackage{wrapfig}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\title{\bf Landslide: Systematic Exploration for Kernel-Space Race Detection}
\author{Ben Blum \and Garth Gibson}
\institute{Computer Science Department, Carnegie Mellon University, Pittsburgh}
\date{May 2012}

%\support{This research was sponsored by the U.S. Army Research Office under grant number W911NF0910273.}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\true{\;\textit{true}}
\newcommand\false{\;\textit{false}}

@@

\begin{abstract}
Systematic exploration is an approach to finding race conditions by deterministically executing many thread interleavings and identifying which ones expose bugs.
Current techniques are suitable for testing user-space programs, but are inadequate for testing kernels.
Testing kernel-level code necessitates understanding the kernel's design in order to effectively control nondeterminism and achieve reasonable state-space reduction.

We present Landslide, a systematic exploration tool for finding races in kernels.
Landslide relies on user-provided configuration to enable efficient exploration and testing of meaningful interleavings.
The user instruments their kernel to inform Landslide of important concurrency events, and configures Landslide to focus its search on relevant kernel components.
This combines the user's design knowledge with Landslide's ability to explore large state spaces, and encourages the user to steer Landslide towards focused searches that are more likely to find bugs.
We claim that this steering is an effective approach for kernel-space race detection.

%Landslide targets Pebbles, the kernel specification that students implement in the undergraduate Operating Systems course at Carnegie Mellon University (15-410).
%We discuss the techniques Landslide uses to address the general challenges of kernel-level concurrency, and we evaluate its effectiveness and usability as a debugging aid.
%We show that our techniques make systematic testing in kernel-space feasible and that Landslide is a useful tool for doing so in the context of 15-410.
%%%%

\noindent {\bf Keywords:} concurrency, kernel debugging, race conditions, runtime verification
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% put this somewhere
%We claim that this combination of the user's knowledge and Landslide's testing mechanisms leads to an effective usage dynamic, in which the user steers Landslide towards focused search spaces that are more likely to find bugs.

@@

%\input{related} % COMPLETE!
%\input{challenges} % COMPLETE!
%\input{terminology} % almost complete
%\input{design}
%\input{using}
%\input{evaluation}
%\input{futurework}
%\input{conclusion}

\bibliography{citations}{}
\bibliographystyle{splncs03}
